Graphs for 1000  Generations

### 2021-07-20 graphs_newt_snakes/fig_1000.Rmd
Added in the results from Peter sugestion about mutation rate. Now I am looking at the differences.

>>>>

# The 12 Starting Points Experiment Redone with Peters SLiM code sugestions!

I was worried about a few confusing parts in the SLiM code that dealt with the mutation rate of newts and snakes (discussed above). Peter suggested:
newt_mu_rate = 1e-10;
snake_mu_rate = 1e-11; 
total_mu_rate = newt_mu_rate + snake_mu_rate:
initializeMutationRate(total_mut_rate);
initializeGenomicElementType("g1", c(m1, m2), c(newt_mu_rate, snake_mu_rate));

Extra note: In my code snake_mu_rate is called mu_rate

```{r 12 points redone data collection, echo=FALSE}

files_1r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_1_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_1r)

newt_max_pheno_1_1r = out[1]
snake_max_pheno_1_1r = out[2]
newt_min_pheno_1_1r  = out[3]
snake_min_pheno_1_1r = out[4]
true_max_1_1r = out[5]
true_min_1_1r = out[6]
min_difference_1_1r = out[7]
max_difference_1_1r = out[8]
my_mean_1r = out[9]
my_sd_1r = out[10]
mean_mean_dif_1r = out[11]
sd_mean_dif_1r = out[12]

print(paste0("Newt max pheno trial 1: ", newt_max_pheno_1_1r))
print(paste0("Snake max phenot trial 1: ", snake_max_pheno_1_1r))
print(paste0("Newt min pheno trial 1: ", newt_min_pheno_1_1r))
print(paste0("Snake min Pheno trial 1: ", snake_min_pheno_1_1r))
print(paste0("Mean of combined snake and newt trial 1: ", my_mean_1r))
print(paste0("Sd of combined snake and newt trial 1: ", my_sd_1r))
print(paste0("Mean of the mean difference trial 1: ", mean_mean_dif_1r))
print(paste0("SD of the mean difference trial 1: ", sd_mean_dif_1r))

files_2r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_2_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_2r)

newt_max_pheno_1_2r = out[1]
snake_max_pheno_1_2r = out[2]
newt_min_pheno_1_2r  = out[3]
snake_min_pheno_1_2r = out[4]
true_max_1_2r = out[5]
true_min_1_2r = out[6]
min_difference_1_2r = out[7]
max_difference_1_2r = out[8]
my_mean_2r = out[9]
my_sd_2r = out[10]
mean_mean_dif_2r = out[11]
sd_mean_dif_2r = out[12]

print(paste0("Newt max pheno trial 2: ", newt_max_pheno_1_2r))
print(paste0("Snake max phenot trial 2: ", snake_max_pheno_1_2r))
print(paste0("Newt min pheno trial 2: ", newt_min_pheno_1_2r))
print(paste0("Snake min Pheno trial 2: ", snake_min_pheno_1_2r))
print(paste0("Mean of combined snake and newt trial 2: ", my_mean_2r))
print(paste0("Sd of combined snake and newt trial 2: ", my_sd_2r))
print(paste0("Mean of the mean difference trial 2: ", mean_mean_dif_2r))
print(paste0("SD of the mean difference trial 2: ", sd_mean_dif_2r))

files_3r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_3_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_3r)

newt_max_pheno_1_3r = out[1]
snake_max_pheno_1_3r = out[2]
newt_min_pheno_1_3r  = out[3]
snake_min_pheno_1_3r = out[4]
true_max_1_3r = out[5]
true_min_1_3r = out[6]
min_difference_1_3r = out[7]
max_difference_1_3r = out[8]
my_mean_3r = out[9]
my_sd_3r = out[10]
mean_mean_dif_3r = out[11]
sd_mean_dif_3r = out[12]

print(paste0("Newt max pheno trial 3: ", newt_max_pheno_1_3r))
print(paste0("Snake max phenot trial 3: ", snake_max_pheno_1_3r))
print(paste0("Newt min pheno trial 3: ", newt_min_pheno_1_3r))
print(paste0("Snake min Pheno trial 3: ", snake_min_pheno_1_3r))
print(paste0("Mean of combined snake and newt trial 3: ", my_mean_3r))
print(paste0("Sd of combined snake and newt trial 3: ", my_sd_3r))
print(paste0("Mean of the mean difference trial 3: ", mean_mean_dif_3r))
print(paste0("SD of the mean difference trial 3: ", sd_mean_dif_3r))

files_4r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_4_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_4r)

newt_max_pheno_1_4r = out[1]
snake_max_pheno_1_4r = out[2]
newt_min_pheno_1_4r  = out[3]
snake_min_pheno_1_4r = out[4]
true_max_1_4r = out[5]
true_min_1_4r = out[6]
min_difference_1_4r = out[7]
max_difference_1_4r = out[8]
my_mean_4r = out[9]
my_sd_4r = out[10]
mean_mean_dif_4r = out[11]
sd_mean_dif_4r = out[12]

print(paste0("Newt max pheno trial 4: ", newt_max_pheno_1_4r))
print(paste0("Snake max phenot trial 4: ", snake_max_pheno_1_4r))
print(paste0("Newt min pheno trial 4: ", newt_min_pheno_1_4r))
print(paste0("Snake min Pheno trial 4: ", snake_min_pheno_1_4r))
print(paste0("Mean of combined snake and newt trial 4: ", my_mean_4r))
print(paste0("Sd of combined snake and newt trial 4: ", my_sd_4r))
print(paste0("Mean of the mean difference trial 4: ", mean_mean_dif_4r))
print(paste0("SD of the mean difference trial 4: ", sd_mean_dif_4r))

files_5r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_5_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_5r)

newt_max_pheno_1_5r = out[1]
snake_max_pheno_1_5r = out[2]
newt_min_pheno_1_5r  = out[3]
snake_min_pheno_1_5r = out[4]
true_max_1_5r = out[5]
true_min_1_5r = out[6]
min_difference_1_5r = out[7]
max_difference_1_5r = out[8]
my_mean_5r = out[9]
my_sd_5r = out[10]
mean_mean_dif_5r = out[11]
sd_mean_dif_5r = out[12]

print(paste0("Newt max pheno trial 5: ", newt_max_pheno_1_5r))
print(paste0("Snake max phenot trial 5: ", snake_max_pheno_1_5r))
print(paste0("Newt min pheno trial 5: ", newt_min_pheno_1_5r))
print(paste0("Snake min Pheno trial 5: ", snake_min_pheno_1_5r))
print(paste0("Mean of combined snake and newt trial 5: ", my_mean_5r))
print(paste0("Sd of combined snake and newt trial 5: ", my_sd_5r))
print(paste0("Mean of the mean difference trial 5: ", mean_mean_dif_5r))
print(paste0("SD of the mean difference trial 5: ", sd_mean_dif_5r))

files_6r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_6_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_6r)

newt_max_pheno_1_6r = out[1]
snake_max_pheno_1_6r = out[2]
newt_min_pheno_1_6r  = out[3]
snake_min_pheno_1_6r = out[4]
true_max_1_6r = out[5]
true_min_1_6r = out[6]
min_difference_1_6r = out[7]
max_difference_1_6r = out[8]
my_mean_6r = out[9]
my_sd_6r = out[10]
mean_mean_dif_6r = out[11]
sd_mean_dif_6r = out[12]

print(paste0("Newt max pheno trial 6: ", newt_max_pheno_1_6r))
print(paste0("Snake max pheno trial 6: ", snake_max_pheno_1_6r))
print(paste0("Newt min pheno trial 6: ", newt_min_pheno_1_6r))
print(paste0("Snake min Pheno  trial 6: ", snake_min_pheno_1_6r))
print(paste0("Mean of combined snake and newt trial 6: ", my_mean_6r))
print(paste0("Sd of combined snake and newt trial 6: ", my_sd_6r))
print(paste0("Mean of the mean difference trial 6: ", mean_mean_dif_6r))
print(paste0("SD of the mean difference trial 6: ", sd_mean_dif_6r))

files_7r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_7_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_7r)

newt_max_pheno_1_7r = out[1]
snake_max_pheno_1_7r = out[2]
newt_min_pheno_1_7r  = out[3]
snake_min_pheno_1_7r = out[4]
true_max_1_7r = out[5]
true_min_1_7r = out[6]
min_difference_1_7r = out[7]
max_difference_1_7r = out[8]
my_mean_7r = out[9]
my_sd_7r = out[10]
mean_mean_dif_7r = out[11]
sd_mean_dif_7r = out[12]

print(paste0("Newt max pheno trial 7: ", newt_max_pheno_1_7r))
print(paste0("Snake max phenot trial 7: ", snake_max_pheno_1_7r))
print(paste0("Newt min pheno trial 7: ", newt_min_pheno_1_7r))
print(paste0("Snake min Pheno trial 7: ", snake_min_pheno_1_7r))
print(paste0("Mean of combined snake and newt trial 7: ", my_mean_7r))
print(paste0("Sd of combined snake and newt trial 7: ", my_sd_7r))
print(paste0("Mean of the mean difference trial 7: ", mean_mean_dif_7r))
print(paste0("SD of the mean difference trial 7: ", sd_mean_dif_7r))

files_8r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_8_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_8r)

newt_max_pheno_1_8r = out[1]
snake_max_pheno_1_8r = out[2]
newt_min_pheno_1_8r  = out[3]
snake_min_pheno_1_8r = out[4]
true_max_1_8r = out[5]
true_min_1_8r = out[6]
min_difference_1_8r = out[7]
max_difference_1_8r = out[8]
my_mean_8r = out[9]
my_sd_8r = out[10]
mean_mean_dif_8r = out[11]
sd_mean_dif_8r = out[12]

print(paste0("Newt max pheno trial 8: ", newt_max_pheno_1_8r))
print(paste0("Snake max phenot trial 8: ", snake_max_pheno_1_8r))
print(paste0("Newt min pheno trial 8: ", newt_min_pheno_1_8r))
print(paste0("Snake min Pheno trial 8: ", snake_min_pheno_1_8r))
print(paste0("Mean of combined snake and newt trial 8: ", my_mean_8r))
print(paste0("Sd of combined snake and newt trial 8: ", my_sd_8r))
print(paste0("Mean of the mean difference trial 8: ", mean_mean_dif_8r))
print(paste0("SD of the mean difference trial 8: ", sd_mean_dif_8r))

files_9r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_9", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_9r)

newt_max_pheno_1_9r = out[1]
snake_max_pheno_1_9r = out[2]
newt_min_pheno_1_9r  = out[3]
snake_min_pheno_1_9r = out[4]
true_max_1_9r = out[5]
true_min_1_9r = out[6]
min_difference_1_9r = out[7]
max_difference_1_9r = out[8]
my_mean_9r = out[9]
my_sd_9r = out[10]
mean_mean_dif_9r = out[11]
sd_mean_dif_9r = out[12]

print(paste0("Newt max pheno trial 9: ", newt_max_pheno_1_9r))
print(paste0("Snake max phenot trial 9: ", snake_max_pheno_1_9r))
print(paste0("Newt min pheno trial 9: ", newt_min_pheno_1_9r))
print(paste0("Snake min Pheno trial 9: ", snake_min_pheno_1_9r))
print(paste0("Mean of combined snake and newt trial 9: ", my_mean_9r))
print(paste0("Sd of combined snake and newt trial 9: ", my_sd_9r))
print(paste0("Mean of the mean difference trial 9: ", mean_mean_dif_9r))
print(paste0("SD of the mean difference trial 9: ", sd_mean_dif_9r))

files_10r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_10_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_10r)

newt_max_pheno_1_10r = out[1]
snake_max_pheno_1_10r = out[2]
newt_min_pheno_1_10r  = out[3]
snake_min_pheno_1_10r = out[4]
true_max_1_10r = out[5]
true_min_1_10r = out[6]
min_difference_1_10r = out[7]
max_difference_1_10r = out[8]
my_mean_10r = out[9]
my_sd_10r = out[10]
mean_mean_dif_10r = out[11]
sd_mean_dif_10r = out[12]

print(paste0("Newt max pheno trial 10: ", newt_max_pheno_1_10r))
print(paste0("Snake max phenot trial 10: ", snake_max_pheno_1_10r))
print(paste0("Newt min pheno trial 10: ", newt_min_pheno_1_10r))
print(paste0("Snake min Pheno trial 10: ", snake_min_pheno_1_10r))
print(paste0("Mean of combined snake and newt trial 10: ", my_mean_10r))
print(paste0("Sd of combined snake and newt trial 10: ", my_sd_10r))
print(paste0("Mean of the mean difference trial 10: ", mean_mean_dif_10r))
print(paste0("SD of the mean difference trial 10: ", sd_mean_dif_10r))

files_11r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_11_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_11r)

newt_max_pheno_1_11r = out[1]
snake_max_pheno_1_11r = out[2]
newt_min_pheno_1_11r  = out[3]
snake_min_pheno_1_11r = out[4]
true_max_1_11r = out[5]
true_min_1_11r = out[6]
min_difference_1_11r = out[7]
max_difference_1_11r = out[8]
my_mean_11r = out[9]
my_sd_11r = out[10]
mean_mean_dif_11r = out[11]
sd_mean_dif_11r = out[12]

print(paste0("Newt max pheno trial 11: ", newt_max_pheno_1_11r))
print(paste0("Snake max phenot trial 11: ", snake_max_pheno_1_11r))
print(paste0("Newt min pheno trial 11: ", newt_min_pheno_1_11r))
print(paste0("Snake min Pheno trial 11: ", snake_min_pheno_1_11r))
print(paste0("Mean of combined snake and newt trial 11: ", my_mean_11r))
print(paste0("Sd of combined snake and newt trial 11: ", my_sd_11r))
print(paste0("Mean of the mean difference trial 11: ", mean_mean_dif_11r))
print(paste0("SD of the mean difference trial 11: ", sd_mean_dif_11r))

files_12r <- list.files(path="~/Desktop/peter_sug_1000", pattern="file_small_trial_12_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_12r)

newt_max_pheno_1_12r = out[1]
snake_max_pheno_1_12r = out[2]
newt_min_pheno_1_12r  = out[3]
snake_min_pheno_1_12r = out[4]
true_max_1_12r = out[5]
true_min_1_12r = out[6]
min_difference_1_12r = out[7]
max_difference_1_12r = out[8]
my_mean_12r = out[9]
my_sd_12r = out[10]
mean_mean_dif_12r = out[11]
sd_mean_dif_12r = out[12]

print(paste0("Newt max pheno trial 12: ", newt_max_pheno_1_12r))
print(paste0("Snake max pheno trial 12: ", snake_max_pheno_1_12r))
print(paste0("Newt min pheno trial 12: ", newt_min_pheno_1_12r))
print(paste0("Snake min Pheno trial 12: ", snake_min_pheno_1_12r))
print(paste0("Mean of combined snake and newt trial 12: ", my_mean_12r))
print(paste0("Sd of combined snake and newt trial 12: ", my_sd_12r))
print(paste0("Mean of the mean difference trial 12: ", mean_mean_dif_12r))
print(paste0("SD of the mean difference trial 12: ", sd_mean_dif_12r))

```{r phenotype graph 12 points redone, echo=FALSE}

title = "Trial 1 Phenotype Measurements for Newts and Snake"
p_1r = phenotype_graph(files_1r, my_mean_1r, my_sd_1r, title)
#p_1

title = "Trial 2 Phenotype Measurements for Newts and Snake"
p_2r = phenotype_graph(files_2r, my_mean_2r, my_sd_2r, title)
#p_2

title = "Trial 3 Phenotype Measurements for Newts and Snake Trial 3"
p_3r = phenotype_graph(files_3r, my_mean_3r, my_sd_3r, title)
#p_3

title = "Trial 4 Phenotype Measurements for Newts and Snake"
p_4r = phenotype_graph(files_4r, my_mean_4r, my_sd_4r, title)
#p_4

grid.arrange(p_1r, p_2r, p_3r, p_4r, nrow = 2)

title = "Trial 5 Phenotype Measurements for Newts and Snake"
p_5r = phenotype_graph(files_5r, my_mean_5r, my_sd_5r, title)
#p_5

title = "Trial 6 Phenotype Measurements for Newts and Snake"
p_6r = phenotype_graph(files_6r, my_mean_6r, my_sd_6r, title)
#p_6

title = "Trial 7 Phenotype Measurements for Newts and Snake"
p_7r = phenotype_graph(files_7r, my_mean_7r, my_sd_7r, title)
#p_7

title = "Trial 8 Phenotype Measurements for Newts and Snake"
p_8r = phenotype_graph(files_8r, my_mean_8r, my_sd_8r, title)
#p_8

grid.arrange(p_5r, p_6r, p_7r, p_8r, nrow=2)

title = "Trial 9 Phenotype Measurements for Newts and Snake"
p_9r = phenotype_graph(files_9r, my_mean_9r, my_sd_9r, title)
#p_9

title = "Trial 10 Phenotype Measurements for Newts and Snake"
p_10r = phenotype_graph(files_10r, my_mean_10r, my_sd_10r, title)
#p_10

title = "Trial 11 Phenotype Measurements for Newts and Snake"
p_11r = phenotype_graph(files_11r, my_mean_11r, my_sd_11r, title)
#p_11

title = "Trial 12  Phenotype Measurements for Newts and Snake"
p_12r = phenotype_graph(files_12r, my_mean_12r, my_sd_12r, title)
#p_12

grid.arrange(p_9r, p_10r, p_11r, p_12r, nrow=2)

```{r 12 sim pheno dif redone, echo=FALSE}

title = "Trial 1: Difference Between Phenotypes (Snakes-Newts)"
d_1r = differnce_graph(files_1r, mean_mean_dif_1r, sd_mean_dif_1r, min_difference_1_1r, max_difference_1_1r, title)

title = "Trial 2: Difference Between Phenotypes (Snakes-Newts)"
d_2r = differnce_graph(files_2r, mean_mean_dif_2r, sd_mean_dif_2r, min_difference_1_2r, max_difference_1_2r, title)

title = "Trial 3: Difference Between Phenotypes (Snakes-Newts)"
d_3r = differnce_graph(files_3r, mean_mean_dif_3r, sd_mean_dif_3r, min_difference_1_3r, max_difference_1_3r, title)

title = "Trial 4: Difference Between Phenotypes (Snakes-Newts)"
d_4r = differnce_graph(files_4r, mean_mean_dif_4r, sd_mean_dif_4r, min_difference_1_4r, max_difference_1_4r, title)

grid.arrange(d_1r, d_2r, d_3r, d_4r, nrow = 2)

title = "Trial 5: Difference Between Phenotypes (Snakes-Newts)"
d_5r = differnce_graph(files_5r, mean_mean_dif_5r, sd_mean_dif_5r, min_difference_1_5r, max_difference_1_5r, title)

title = "Trial 6: Difference Between Phenotypes (Snakes-Newts)"
d_6r = differnce_graph(files_6r, mean_mean_dif_6r, sd_mean_dif_6r, min_difference_1_6r, max_difference_1_6r, title)

title = "Trial 7: Difference Between Phenotypes (Snakes-Newts)"
d_7r = differnce_graph(files_7r, mean_mean_dif_7r, sd_mean_dif_7r, min_difference_1_7r, max_difference_1_7r, title)

title = "Trial 8: Difference Between Phenotypes (Snakes-Newts)"
d_8r = differnce_graph(files_8r, mean_mean_dif_8r, sd_mean_dif_8r, min_difference_1_8r, max_difference_1_8r, title)

grid.arrange(d_5r, d_6r, d_7r, d_8r, nrow = 2)

title = "Trial 9: Difference Between Phenotypes (Snakes-Newts)"
d_9r = differnce_graph(files_9r, mean_mean_dif_9r, sd_mean_dif_9r, min_difference_1_9r, max_difference_1_9r, title)

title = "Trial 10: Difference Between Phenotypes (Snakes-Newts)"
d_10r = differnce_graph(files_10r, mean_mean_dif_10r, sd_mean_dif_10r, min_difference_1_10r, max_difference_1_10rr, title)

title = "Trial 11: Difference Between Phenotypes (Snakes-Newts)"
d_11r = differnce_graph(files_11r, mean_mean_dif_11r, sd_mean_dif_11r, min_difference_1_11r, max_difference_1_11r, title)

title = "Trial 12: Difference Between Phenotypes (Snakes-Newts)"
d_12r = differnce_graph(files_12r, mean_mean_dif_12r, sd_mean_dif_12r, min_difference_1_12r, max_difference_1_12r, title)

grid.arrange(d_9r, d_10r, d_11r, d_12r, nrow = 2)

```{r 12 sim pheno change redone, echo=FALSE}

title = "Trial 1 12sim: Phenotype Change"
c_1r=phenotype_change_graph(files_1r, my_mean_1r, my_sd_1r, title)

title = "Trial 2 12sim: Phenotype Change"
c_2r=phenotype_change_graph(files_2r, my_mean_2r, my_sd_2r, title)

title = "Trial 3 12sim: Phenotype Change"
c_3r=phenotype_change_graph(files_3r, my_mean_3r, my_sd_3r, title)

title = "Trial 4 12sim: Phenotype Change"
c_4r=phenotype_change_graph(files_4r, my_mean_4r, my_sd_4r, title)

grid.arrange(c_1r, c_2r, c_3r, c_4r, nrow = 2)

title = "Trial 5 12sim: Phenotype Change"
c_5r=phenotype_change_graph(files_5r, my_mean_5r, my_sd_5r, title)

title = "Trial 6 12sim: Phenotype Change"
c_6r=phenotype_change_graph(files_6r, my_mean_6r, my_sd_6r, title)

title = "Trial 7 12sim: Phenotype Change"
c_7r=phenotype_change_graph(files_7r, my_mean_7r, my_sd_7r, title)

title = "Trial 8 12sim: Phenotype Change"
c_8r=phenotype_change_graph(files_8r, my_mean_8r, my_sd_8r, title)

grid.arrange(c_5r, c_6r, c_7r, c_8r, nrow = 2)

title = "Trial 9 12sim: Phenotype Change"
c_9r=phenotype_change_graph(files_9r, my_mean_9r, my_sd_9r, title)

title = "Trial 10 12sim: Phenotype Change"
c_10r=phenotype_change_graph(files_10r, my_mean_10r, my_sd_10r, title)

title = "Trial 11 12sim: Phenotype Change"
c_11r=phenotype_change_graph(files_11r, my_mean_11r, my_sd_11r, title)

title = "Trial 12 12sim: Phenotype Change"
c_12r=phenotype_change_graph(files_12r, my_mean_12r, my_sd_12r, title)

grid.arrange(c_9r, c_10r, c_11r, c_12r, nrow = 2)

```{r 12 point trasformation redone, echo=FALSE}

title1 = "Trial 1: Newt trasnformed vs un-trasformed"
title2 = "Trial 1: Snake trasnformed vs un-trasformed"
graph_1r = untrasform(files_1r, my_mean_1r, my_sd_1r, title1, title2, is_log=FALSE)

title1 = "Trial 2: Newt trasnformed vs un-trasformed"
title2 = "Trial 2: Snake trasnformed vs un-trasformed"
graph_2r = untrasform(files_2r, my_mean_2r, my_sd_2r, title1, title2, is_log=FALSE)

title1 = "Trial 3: Newt trasnformed vs un-trasformed"
title2 = "Trial 3: Snake trasnformed vs un-trasformed"
graph_3r = untrasform(files_3r, my_mean_3r, my_sd_3r, title1, title2, is_log=FALSE)

title1 = "Trial 4: Newt trasnformed vs un-trasformed"
title2 = "Trial 4: Snake trasnformed vs un-trasformed"
graph_4r = untrasform(files_4r, my_mean_4r, my_sd_4r, title1, title2, is_log=FALSE)

grid.arrange(graph_1r[[1]], graph_1r[[2]], graph_2r[[1]], graph_2r[[2]], graph_3r[[1]], graph_3r[[2]], graph_4r[[1]], graph_4r[[2]], nrow = 4)

title1 = "Trial 5: Newt trasnformed vs un-trasformed"
title2 = "Trial 5: Snake trasnformed vs un-trasformed"
graph_5r = untrasform(files_5r, my_mean_5r, my_sd_5r, title1, title2, is_log=FALSE)

title1 = "Trial 6: Newt trasnformed vs un-trasformed"
title2 = "Trial 6: Snake trasnformed vs un-trasformed"
graph_6r = untrasform(files_6r, my_mean_6r, my_sd_6r, title1, title2, is_log=FALSE)

title1 = "Trial 7: Newt trasnformed vs un-trasformed"
title2 = "Trial 7: Snake trasnformed vs un-trasformed"
graph_7r = untrasform(files_7r, my_mean_7r, my_sd_7r, title1, title2, is_log=FALSE)

title1 = "Trial 8: Newt trasnformed vs un-trasformed"
title2 = "Trial 8: Snake trasnformed vs un-trasformed"
graph_8r = untrasform(files_8r, my_mean_8r, my_sd_8r, title1, title2, is_log=FALSE)

grid.arrange(graph_5r[[1]], graph_5r[[2]], graph_6r[[1]], graph_6r[[2]], graph_7r[[1]], graph_7r[[2]], graph_8r[[1]], graph_8r[[2]], nrow = 4)

title1 = "Trial 9: Newt trasnformed vs un-trasformed"
title2 = "Trial 9: Snake trasnformed vs un-trasformed"
graph_9r = untrasform(files_9r, my_mean_9r, my_sd_9r, title1, title2, is_log=FALSE)

title1 = "Trial 10: Newt trasnformed vs un-trasformed"
title2 = "Trial 10: Snake trasnformed vs un-trasformed"
graph_10r = untrasform(files_10r, my_mean_10r, my_sd_10r, title1, title2, is_log=FALSE)

title1 = "Trial 11: Newt trasnformed vs un-trasformed"
title2 = "Trial 11: Snake trasnformed vs un-trasformed"
graph_11r = untrasform(files_11r, my_mean_11r, my_sd_11r, title1, title2, is_log=FALSE)

title1 = "Trial 12: Newt trasnformed vs un-trasformed"
title2 = "Trial 12: Snake trasnformed vs un-trasformed"
graph_12r = untrasform(files_12r, my_mean_12r, my_sd_12r, title1, title2, is_log=FALSE)

grid.arrange(graph_9r[[1]], graph_9r[[2]], graph_10r[[1]], graph_10r[[2]], graph_11r[[1]], graph_11r[[2]], graph_12r[[1]], graph_12r[[2]], nrow = 4)
